\documentclass[]{article}
\usepackage{xeCJK}
%opening
\title{Computer Networking: A Top-Down Approach \\ Homework 2}
\author{Class 42 \\ 欧阳鹏程 \\ 2141601030 \\ Copyright Notice: BY-NC-SA}

\begin{document}

\maketitle

\section{Additional Problems}
\begin{enumerate}
	\item Explain precisely following abbreviations:
	\subitem URL, HTML, RTT, MIME, TFTP, NFS, SNMP, JPEG, MPEG
	
	\item Specify following system Organization:
	\subitem Email system, DNS system
\end{enumerate}

\section{Problems on textbooks}
\begin{enumerate}
	\item[R1.] P1. True or false?
	a. A user requests a Web page that consists of some text and three images.
	For this page, the client will send one request message and receive four
	response messages.
	b. Two distinct Web pages (for example, www.mit.edu/research.html
	and www.mit.edu/students.html) can be sent over the same persistent connection.
	c. With nonpersistent connections between browser and origin server, it is possible for a single TCP segment to carry two distinct HTTP request messages.
	d. The Date: header in the HTTP response message indicates when the
	object in the response was last modified.
	
	\item[R6.] P6. Obtain the HTTP/1.1 specification (RFC 2616). Answer the following questions:
	a. Explain the mechanism used for signaling between the client and server
	to indicate that a persistent connection is being closed. Can the client, the
	server, or both signal the close of a connection?
	b. What encryption services are provided by HTTP?
	c. Can a client open three or more simultaneous connections with a given
	server?
	d. Either a server or a client may close a transport connection between them
	if either one detects the connection has been idle for some time. Is it possible that one side starts closing a connection while the other side is transmitting data via this connection? Explain.
\end{enumerate}

\section{Discussion}
\begin{enumerate}
	\item[D6.] What is the Apache Web server? How much does it cost? What functionality does it currently have?
\end{enumerate}

\end{document}
